Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-11 paper/paper.tex
pass

\subsection{\Fix{JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit}}
\label{sec:content-example}
\Luc{JBoss é um servidor de aplicação Java muito popular, de codigo aberto. Esse ataque tem como alvo esses servidores e permite que seja feita execução remota de comandos. Os pacotes que estamos utilizando para testar esse ataque foram gerados pelo Nikto, mas o Metasploit tambem possui um modulo para ele. A regra de ouro para esse ataque é:

@@

\begin{theorem}
  The minimization algorithm computes rules that capture only
  the positive traffic.
\end{theorem}
\begin{proof}
  Every rule created during the search captures the positive traffic
  as every rule contains a proper subset of the option from the
  original rule and all those options are satisfied by the positive
  traffic. By definition of function $\mathit{isfit}$, these rules
  also capture \emph{only} the positive traffic. If some negative
  traffic was captured, a rule would not be added to $\mathcal
  R'$.
\end{proof}

@@

\Mar{------------------------------------ estou aqui}

\Luc{Componente 1: Tamanho da regra.
\begin{figure}[H]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rule-size}Number of rules per number of options.}
\end{figure}

@@

}
\Fix{...elaborate...}

>>>>

\subsection{\Fix{JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit}}
\label{sec:content-example}

\Mar{Note que a gente organizou estas secoes por tipo de ataque. Este
  titulo eh muito especifico.}
\Luc{JBoss é um servidor de aplicação Java muito popular, de codigo aberto. Esse ataque tem como alvo esses servidores e permite que seja feita execução remota de comandos. Os pacotes que estamos utilizando para testar esse ataque foram gerados pelo Nikto, mas o Metasploit tambem possui um modulo para ele. A regra de ouro para esse ataque é:

@@

\begin{theorem}
  The minimization algorithm computes rules that capture only
  the positive traffic.
\end{theorem}
\begin{proof}
  Every rule created during the search captures the positive traffic
  as every rule contains a proper subset of the option from the
  original rule and all those options are satisfied by the positive
  traffic. By definition of function $\mathit{isPlausible}$, these rules
  also capture \emph{only} the positive traffic. If some negative
  traffic was captured, a rule would not be added to $\mathcal
  R'$.
\end{proof}

@@

\tname{} uses a composition of heurisitc functions to sort the rules
it produces. Each function uses a different criterion to estimate how
similar a rule created in the previous step is to existing Suricata
rules~\cite{emerging-threats-open}. We describe in the following each
of these heuristic functions. Each function $f_i$ ranges in the 0-1
domain. \tname{} uses the weighted average of these functions to sort
rules: $\sum{f_i}/|f_i|$.

\subsubsection{Size of a rule}
\tname{} uses the size of existing rules as a heuristic function. For
example, we noted that most rules in the dataset have 2 to 5 options,
so \tname{} values rules in this size range higher compared to other
sizes. Figure~\ref{fig:distribution-rule-size} shows the histogram of
rule sizes. The x-axis shows the number of options (\ie{}, size)
included in a rule and the y-axis shows the number of rules that have
that number of options. \tname{} uses this information to rank rules.

\begin{figure}[H]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.09,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rule-size}Distribution of rule
    size.\Mar{how is it possible a rule with 0 options?}}
\end{figure}

\Mar{----------------------------------------- estou aqui}

@@
